---
title: "Data set creation"
author: "marie"
date: "2024-06-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

Now that we have found the articles in arxiv, we want to re-sort the documents into double and single blind
```{r}
df = read.csv("data/original/df_submission_rating.csv", header = T)
df2018 = read.csv("data/arxiv_results_2018.csv", header = T)

#ensure correct formatting of date
df2018$submitted_date <- as.POSIXct(df2018$submitted, format="%Y-%m-%d %H:%M:%S")
```

Set the date that we want to use as the before/after marker for single vs. double blind. 

Options are:

- Nov. 28, 2017 : reviewer initial deadline
- Jan. 6, 2018 : rebuttal period
- Jan. 30, 2018 : decision

Change both target date and folder name to write correct dataset. 

Submitted comp will included whether the date submitted to arxiv was before (single blind) or after (double blind) the indicated date. NA indicates that entry was not found in ArXiV. 

This RMD has been run three times, once each using the appropriate date. 

```{r}
target_date <- as.POSIXct("2017-11-28 00:00:00")
folder = "decision_"

df2018$submitted_comp <- ifelse(
  is.na(df2018$submitted_date), "na", if_else(
    df2018$submitted_date < target_date, "before", ifelse(
      df2018$submitted_date == target_date,  "on",  "after")
  )
)
```

```{r}
df2018 |> group_by(submitted_comp) |>
  summarise(count = n(), 
            score = mean(score)) 
```

Look at scores of data in three categories. 

```{r}
df2018 |> ggplot(aes(x = score, color = submitted_comp)) +
  geom_density()
```

We see something weird - the scores of entries not found on arxiv are overall notably lower than both categories of those that are found. 

# Data set creation

Below, conf_year has vaues 2017 as a proxy for single blind; 2018 is a proxy for double blind.  
We will create a new column iclr_year to preserve the original (true) year.

```{r}
df$iclr_year = df$conf_year
```

## 2018 ONLY : all rows

This dataset (all_2018) looks only at papers submitted to ICLR2018. Papers submitted to ICLR2017 have conf_year set to 0. 

```{r}
df <- df %>%
  mutate(conf_year = ifelse(iclr_year == 2017, 0, conf_year))
```


```{r}
# Merge df and df2018 to get submitted_comp for iclr_year 2018
df <- df %>%
  left_join(df2018 %>% select(id, submitted_comp), by = "id") %>%
  mutate(conf_year = ifelse(iclr_year == 2018, submitted_comp, conf_year)) %>%
  select(-submitted_comp) |> # Remove the column if it's no longer needed 
  mutate(conf_year = case_when(
    conf_year == "after" ~ "2018",
    conf_year == "before" ~ "2017",
    conf_year == "na" ~ "2018",
    TRUE ~ conf_year  # keep the original value if no match
  ))
```

```{r}
df |> group_by(conf_year) |>summarise(n = n())
```

```{r}
path = paste0("data/", folder, "all_2018/df_submission_rating.csv")
write.csv(df, path, row.names = FALSE)
```


## 2018 ONLY : only rows found on arxiv

This dataset (found_2018) looks only at papers submitted to ICLR2018 AND found on ArXiV. 

Papers submitted to ICLR2017 have conf_year set to 0. 
Papers submitted to ICLR2018 but not found on ArXiV have conf_year set to 1.

```{r}
#ids of rows not matched in the arxiv search
id_list <- df2018 %>%
  filter(is.na(matched_title)) %>%
  select(id) %>%
  pull()
```

```{r}
df$conf_year[df$id %in% id_list] <- 1
```

```{r}
path = paste0("data/", folder, "found_2018/df_submission_rating.csv")
write.csv(df, path, row.names = FALSE)
```


## 2018 and 2017 : all

This data set (all_2017_2018) is the same as all_2018 but includes the original ICLR2017 submissions

```{r}
#clean start on df
df = read.csv("data/original/df_submission_rating.csv", header = T)
```

```{r}
df$iclr_year = df$conf_year
```

```{r}
# Merge df and df2018 to get submitted_comp for iclr_year 2018
df <- df %>%
  left_join(df2018 %>% select(id, submitted_comp), by = "id") %>%
  mutate(conf_year = ifelse(iclr_year == 2018, submitted_comp, conf_year)) %>%
  select(-submitted_comp) |> # Remove the column if it's no longer needed 
  mutate(conf_year = case_when(
    conf_year == "after" ~ "2018",
    conf_year == "before" ~ "2017",
    conf_year == "na" ~ "2018",
    TRUE ~ conf_year  # keep the original value if no match
  ))
```




```{r}
path = paste0("data/", folder, "all_2017_2018/df_submission_rating.csv")
write.csv(df, path, row.names = FALSE)
```

## 2018 and 2017 : only keeping 2018 rows that were found

This data set (all_2017_found_2018) is the same as found_2018 but includes the original ICLR2017 submissions


```{r}
#ids of rows not matched in the arxiv search
id_list <- df2018 %>%
  filter(is.na(matched_title)) %>%
  select(id) %>%
  pull()
```

```{r}
df$conf_year[df$id %in% id_list] <- 1
```

```{r}
path = paste0("data/", folder, "all_2017_found_2018/df_submission_rating.csv")
write.csv(df, path, row.names = FALSE)
```



### Check datasets

```{r}
df_test = read.csv("data/reviewer_all_2017_2018/df_submission_rating.csv", header = T)
```

```{r}
df_test |> group_by(conf_year) |>
  summarise(count = n()) 
```
