---
title: "analysis"
author: "marie"
date: "2024-06-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## setup and load data
```{r}
library(tidyverse)
```



## score information

```{r}
library(ggplot2)

# Assuming df_arx is your dataframe

# Plot with density plot
ggplot(df_arx, aes(x = score, color = submitted_comp)) +
  geom_density() +
  scale_color_manual(values = c("before" = "darkgreen", "after" = "hotpink"),
                     breaks = c("before", "after"),
                     labels = c("2017", "2018")) +
  labs(color = "Submitted Year")

# Plot with boxplot
ggplot(df_arx, aes(x = score, color = submitted_comp)) +
  geom_boxplot() +
  scale_color_manual(values = c("before" = "darkgreen", "after" = "hotpink"),
                     breaks = c("before", "after"),
                     labels = c("2017", "2018")) +
  labs(color = "Submitted Year")

```


Red line is double blind, blue line is single blind. Initially, looks like at least correlational support of claim about higher scores with single blind.
```{r}
df |> ggplot(aes(x = AVG_rating, color = as.factor(conf_year))) +
  geom_density() +
  scale_color_manual(values = c("2017" = "darkgreen", "2018" = "hotpink"))

df |> ggplot(aes(x = AVG_rating, color = as.factor(conf_year))) +
  geom_boxplot() +
  scale_color_manual(values = c("2017" = "darkgreen", "2018" = "hotpink"))
```

Interesting idea: 

- get some sort of degree of author success (ie h-index or citations...); look at max author success on a given paper. examine differences
- this information could probably be scraped from google scholar. 
- issues of note: some papers no author has clickable profile. also, differing email addressses. 

