---
title: "test_author"
author: "marie"
date: "2024-07-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

```{r}
#look at reviewer data set

folder = "reviewer_"
df_author = read.csv(paste0("data/", folder, "found_2018/df_submission_rating.csv"))

df_author <- df_author |>
  mutate(sub_type = recode(as.factor(conf_year),
                            `0` = "ICLR 2017",
                            `1` = "ICLR 2018 : Not Found",
                            `2017` = "ICLR 2018 : Single",
                            `2018` = "ICLR 2018 : Double"))

df_author_test = df_author


df_author_test$authors_list <- lapply(df_author_test$authorids, function(x) {
  # Remove the square brackets and split the string by comma
  author_ids <- unlist(strsplit(gsub("\\[|\\]|\"", "", x), ", "))
  #print(author_ids)
  return(author_ids)
})

# Unlist all authors into a single vector
all_authors <- unlist(df_author_test$authors_list)

# Count occurrences of each author and filter those with more than one appearance
author_counts <- data.frame(table(all_authors))
unique_authors <- author_counts[author_counts$Freq == 1, ]
multiple_authors <- author_counts[author_counts$Freq > 1, ]

```


```{r}
df_author_2018 = df_author_test[df_author_test$iclr_year == 2018,]
df_author_2018s = df_author_test[df_author_test$sub_type == "ICLR 2018 : Single",]
df_author_2018d = df_author_test[df_author_test$sub_type == "ICLR 2018 : Double",]
df_author_2018na = df_author_test[df_author_test$sub_type == "ICLR 2018 : Not Found",]
```

#all 2018 authors
```{r}
df_author_2018$authors_list <- lapply(df_author_2018$authorids, function(x) {
  # Remove the square brackets and split the string by comma
  author_ids <- unlist(strsplit(gsub("\\[|\\]|\"", "", x), ", "))
  #print(author_ids)
  return(author_ids)
})

# Unlist all authors into a single vector
authors_2018 <- unlist(df_author_2018$authors_list)
authors_2018_unique = unique(authors_2018)

authors_2018_counts <- data.frame(table(authors_2018))

```

#get list of authors in single blind
```{r}
df_author_2018s$authors_list <- lapply(df_author_2018s$authorids, function(x) {
  # Remove the square brackets and split the string by comma
  author_ids <- unlist(strsplit(gsub("\\[|\\]|\"", "", x), ", "))
  #print(author_ids)
  return(author_ids)
})

# Unlist all authors into a single vector
authors_2018s <- unlist(df_author_2018s$authors_list)
authors_2018s_unique = unique(authors_2018s)

authors_2018s_counts <- data.frame(table(authors_2018s))


```

#get list of authors in double blind
```{r}
df_author_2018d$authors_list <- lapply(df_author_2018d$authorids, function(x) {
  # Remove the square brackets and split the string by comma
  author_ids <- unlist(strsplit(gsub("\\[|\\]|\"", "", x), ", "))
  #print(author_ids)
  return(author_ids)
})

# Unlist all authors into a single vector
authors_2018d <- unlist(df_author_2018d$authors_list)
authors_2018d_unique = unique(authors_2018d)

authors_2018d_counts <- data.frame(table(authors_2018d))

```

#get list of authors in not found
```{r}
df_author_2018na$authors_list <- lapply(df_author_2018na$authorids, function(x) {
  # Remove the square brackets and split the string by comma
  author_ids <- unlist(strsplit(gsub("\\[|\\]|\"", "", x), ", "))
  #print(author_ids)
  return(author_ids)
})

# Unlist all authors into a single vector
authors_2018na <- unlist(df_author_2018na$authors_list)
authors_2018na_unique = unique(authors_2018na)

authors_2018na_counts <- data.frame(table(authors_2018na))

```


# create overall author info data frame

```{r}
author_info_2018 = data.frame(author_id = authors_2018_unique)
author_info_2018$single = 0
author_info_2018$double = 0
author_info_2018$na = 0
author_info_2018$total = 0
```


```{r}
#change to lapply
for(i in 1:nrow(author_info_2018)){
  
  author = author_info_2018$author_id[i]
  
  s = authors_2018s_counts[authors_2018s_counts$authors_2018 == author, "Freq"]
  d = authors_2018d_counts[authors_2018d_counts$authors_2018 == author, "Freq"]
  na = authors_2018na_counts[authors_2018na_counts$authors_2018 == author, "Freq"]
  tot = authors_2018_counts[authors_2018_counts$authors_2018 == author, "Freq"]
  
  author_info_2018$single[i] = ifelse(length(s) > 0, s, 0)
  author_info_2018$double[i] = ifelse(length(d) > 0, d, 0)
  author_info_2018$na[i] = ifelse(length(na) > 0, na, 0)
  author_info_2018$total[i] = tot
  
}
```

```{r}
author_info_2018_na_overlap <- author_info_2018 %>%
  filter(na > 0, single > 0 | double > 0)

nrow(author_info_2018_na_overlap)
nrow(author_info_2018)
```

only 196 out of 2770 authors appeared in both a not found row and a single or double blind row

Now, let's check the author status of the NA papers

```{r}
df_author_2018na$num_author = 0
df_author_2018na$num_single = 0
df_author_2018na$num_double = 0
```

```{r}
for (i in 1:nrow(df_author_2018na)) {
  author_list = unlist(df_author_2018na$authors_list[i])
  ns = 0
  nd = 0
  for (an in 1:length(author_list)) {
    a = author_list[an]
    if (a %in% authors_2018s_unique) {ns = ns + 1 }
    if (a %in% authors_2018d_unique) {nd = nd + 1 }
  }
  df_author_2018na$num_author[i] = length(author_list)
  df_author_2018na$num_single[i] = ns
  df_author_2018na$num_double[i] = nd
}
```

```{r}
count_na_single <- df_author_2018na %>%
  filter(num_single > 0 & num_double == 0) %>%
  summarise(count = n()) %>%
  pull(count)

count_na_double <- df_author_2018na %>%
  filter(num_single == 0 & num_double > 0) %>%
  summarise(count = n()) %>%
  pull(count)

count_na_double_single <- df_author_2018na %>%
  filter( num_single > 0 & num_double > 0) %>%
  summarise(count = n()) %>%
  pull(count)

count_na_no_overlap <- df_author_2018na %>%
  filter(num_single  == 0 & num_double == 0) %>%
  summarise(count = n()) %>%
  pull(count)

count_na_single
count_na_double
count_na_double_single
count_na_no_overlap
```

Look at distribution of these categories above!
```{r}

df_author_2018na <- df_author_2018na %>%
  mutate(type_of_overlap = case_when(
    num_single > 0 & num_double == 0 ~ "na_single",
    num_single == 0 & num_double > 0 ~ "na_double",
    num_single > 0 & num_double > 0 ~ "na_single_double",
    num_single == 0 & num_double == 0 ~ "na_no_overlap"
  ))
```


```{r}
# Convert type_of_overlap to a factor with the specified order
df_author_2018na$type_of_overlap <- factor(df_author_2018na$type_of_overlap, 
                                           levels = c("na_single", "na_double", "na_single_double", "na_no_overlap"))

# Create the boxplot with the specified order
df_author_2018na_box = df_author_2018na |> 
  ggplot(aes(x = AVG_rating, color = type_of_overlap)) + 
  geom_boxplot() +
  scale_color_manual(values=c("royalblue4", "dodgerblue3", "lightskyblue2", "turquoise4"))+
  theme(axis.text.y=element_blank())+
  theme(axis.ticks.y=element_blank()) +
  labs(color = "Category") 


df_author_2018na_box
ggsave("boxscores_author.pdf", plot = df_author_2018na_box, width=8, height=3, dpi=300)

```


what if single overlap is really single?

```{r}
# Get the ids where type_of_overlap is "na_single"
ids_na_single <- df_author_2018na$id[df_author_2018na$type_of_overlap == "na_single"]

df_author_update = read.csv(paste0("data/", folder, "found_2018/df_submission_rating.csv"))
# Update conf_year to 2017 for rows in df with matching ids
df_author_update$conf_year[df_author_update$id %in% ids_na_single] <- 2017
```

```{r}
df_author_update |> group_by(conf_year) |>
  summarise(count = n())
```

```{r}
write.csv(df_author_update, paste0("data/", folder, "found_2018_author/df_submission_rating.csv"))
```



```{r}
# Get the ids where type_of_overlap is "na_single"
ids_na_single <- df_author_2018na$id[df_author_2018na$type_of_overlap == "na_single"]

df_author_update = read.csv(paste0("data/", folder, "all_2017_2018/df_submission_rating.csv"))
# Update conf_year to 2017 for rows in df with matching ids
df_author_update$conf_year[df_author_update$id %in% ids_na_single] <- 2017
```

```{r}
df_author_update |> group_by(conf_year) |>
  summarise(count = n())
```

```{r}
write.csv(df_author_update, paste0("data/", folder, "all_2017_2018_author/df_submission_rating.csv"))
```
