---
title: "data_clean_R2"
author: "marie"
date: "2024-06-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# setup

load packages and read data

```{r}
library(tidyverse)
library(aRxiv)

df = read.csv("data/original/df_submission_rating.csv", header = T)
df2018 = df[df$conf_year == 2018,]
```

# Perform scraping - search for each title in ArXiV!!

create search title queries
```{r}
df2018$query_title = trimws(df2018$title)
df2018$query_title = gsub('[[:punct:] ]+', " ", df2018$title)
```

## make what will eventually be results dataframe
```{r}
df_results_2 = data
df_results_2 = data.frame(title = df2018$title, 
                        authors = df2018$authors,
                        matched_title = NA,
                        matched_author = NA,
                        submitted = NA,
                        updated = NA, 
                        score = df2018$AVG_rating,
                        num_reviews = df2018$NUM_Reviews,
                        id = df2018$id
                        )

df_results_2$arx_id = NA
df_results_2$arx_id_match = NA

#this identifies match type
df_results_2$match_type = "automatic"
```

## function definitions
```{r}
# Function to clean strings
clean_string <- function(string) {
  # Remove punctuation
  string <- str_replace_all(string, "[[:punct:]]", "")
  # Remove whitespace
  string <- str_replace_all(string, "\\s+", "")
  # Convert to lower case
  string <- tolower(string)
  return(string)
}

# Function to search and match titles using arxiv api
# this does exact title match; should ignore punctuation, but we get weird results
search_and_match <- function(title) {
    search_results <- arxiv_search(query = paste0("ti:\"", title, "\""))
    search_results$title <- gsub("\n ", "", search_results$title)
    exact_matches <- search_results[clean_string(search_results$title) == clean_string(title), ]
    return(exact_matches)
}


contains_punctuation <- function(text) {
  return(grepl("[[:punct:]]", text))
}
```


## perform initial scraping
```{r}
for (i in 890:nrow(df2018)){
 
  exact_title <- df2018$query_title[i]
  test_title = df2018$title[i]
  
  # Search and attempt to match with the title, stripped of punctuation
  exact_matches <- search_and_match(exact_title)
  
  # If exact match is not found and title contains punctuation
  # this helps navigate some weird punctuation errors in search 
  # sometimes punctuation is needed, sometimes it is not
  if (nrow(exact_matches) == 0 && contains_punctuation(test_title)) {
    exact_matches <- search_and_match(test_title)
  }
  
  # If an exact match is found, store results
  if (nrow(exact_matches) == 1) {
    df_results_2$matched_title[i] <- exact_matches$title
    df_results_2$matched_author[i] <- exact_matches$authors
    df_results_2$submitted[i] <- exact_matches$submitted
    df_results_2$updated[i] <- exact_matches$updated
    df_results_2$arx_id_match[i] <- exact_matches$id
  }
  
  print(i)
  print(test_title)
  print(nrow(exact_matches))
  print("---------")
}
  

```


```{r}
not_found_r2 = df_results_2[is.na(df_results_2$matched_title),]
found_r2 = df_results_2[!is.na(df_results_2$matched_title),]

not_found_r2.idx = as.numeric(rownames(not_found_r2))
```

# add any manual matches 
The manual matches are found by hand by searching arxiv's website. 
Currently, I only include exact matches that were not found due to weird punctuation issues. Going forward, I want to include other misc. titles that are more of a fuzzy match. 

Eventually, it would be nice for this to be done with a fuzzy search/scraping. This is currently sufficient for data exploration purposes.

```{r}
#load in manual match csv
manual_data = read.csv("manual_match.csv", header = T, colClasses = c("character", "character"))
manual_data$id = as.character(manual_data$id)
```

```{r}
for(j in 1:nrow(manual_data)){
  i = as.integer(manual_data$rowname[j])
  search_results_id = arxiv_search(query = paste("id:", manual_data$id[j], sep = ""))
  df_results_2$matched_title[i] <- search_results_id$title
  df_results_2$matched_author[i] <- search_results_id$authors
  df_results_2$submitted[i] <- search_results_id$submitted
  df_results_2$updated[i] <- search_results_id$updated
  df_results_2$match_type[i] <- manual_data$type[j]
  df_results_2$arx_id[i] <- manual_data$id[j]
  df_results_2$arx_id_match[i] <- search_results_id$id
}
```


# save CSV

```{r}
write.csv(df_results_2, "arxiv_results_2018.csv", row.names = FALSE)
```
